{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-30 bmvc_review.tex
Revised the drafts on the comments.

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and the theory and its work flow has been detailed in
other papers already \cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation
filter framework representing training examples as a circulant matrix. To reduce complexity, the
circulant matrix can be diagonalized by Discrete Fourier Transform.  This way, off-diagonal elements become
zero whereas the diagonal elements represent the eigenvalues of the circulant matrix. The egienvalues are equal
to the DFT transformation of the base sample ($x$) elements. The Kernelized Correlation Filter, on the other hand,
applies a kernel to $x$ to transform to a more discriminative domain. The circulant matrix is then formed by applying
cylic shifts on the kernelized $x$. Such kernelization operation does not introduce additional complexity to the baseline
correlation filter framework.

{\it Burak: The above paragraph didn't connect to the following
  paragraphs. You'll have to finish up the sentence about a
  correlation filter's, not KCF yet, computational efficiency and then
  continue to explain how this a regularized correlation filter will
  be transformed into KCF w/ the same computational complexity.}

{\it YoungWoo : I edited it based on your comment}

The KCF essentially solves the problem of a regression in the form of
the regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
multiplication in frequency domain was proposed as a sub-linear
solution for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
In fact, a non-linear version of this closed-form solution is proposed
to make it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as 
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
public, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We
aims at developing an object tracking algorithm that ``efficiently''
runs on an embedded system in ``high speed,'' $\ge 300$ fps, e.g.,
running our tracking algorithms on a drone. Given this, we believe
that the UAV123 video data is a better fit in evaluating the
performance of the proposed algorithm than any other existing tracking
datasets. This is because there are many challenging scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is important to compare the performance of the
proposed algorithm with those of the state-of-the-art in nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Finally, the {\it E}nKCF2 is tested on temporally
down-sampled version of the UAV123 dataset, called UAV123$\_$10fps dataset. 
This way, by modifying the proposed {\it E}nKCF framework slightly we can tackle scenarios dominated by extreme camera and object
motion as we run multiple correlation filter at each frame. One can also perform such modifications based on the hardware specifications. 
A more sophisticated hardware can be more friendly to apply multiple correlation filter ({\it E}nKCF2) at one frame
whereas the ones on the low end can only accommodate a single correlation filter at each frame ({\it E}nKCF).

{\it Burak: You need to explain why it is useful or meaningful to
  evaluate our algorithm w/ a down-sampled version of the UAV123
  dataset.}

{\it YoungWoo: I edited the preceding paragraph based on your comment.}

@@

{\it Burak: I don't think I agreed to put the following part as a part
  of our submission.}

>>>>

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and its work flow has been detailed in other papers
already \cite{henriques2012exploiting,henriques2015high}. This section
briefly goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The egienvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cylic shifts on the kernelized $x$. Such kernelization operation does
not introduce additional complexity to the baseline correlation filter
framework.
\begin{comment}
{\it Burak: The above paragraph didn't connect to the following
  paragraphs. You'll have to finish up the sentence about a
  correlation filter's, not KCF yet, computational efficiency and then
  continue to explain how this a regularized correlation filter will
  be transformed into KCF w/ the same computational complexity.}

{\it YoungWoo : I edited it based on your comment}
\end{comment}
The KCF essentially solves the problem of a regression in the form of
the regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
multiplication in frequency domain was proposed as a sub-linear
solution for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
In fact, a non-linear version of this closed-form solution is proposed
to make it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as 
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
public, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We
aims at developing an object tracking algorithm that ``efficiently''
runs on an embedded system (e.g., a drone) in ``high speed,'' $\ge
300$ fps, e.g. Given this, we believe that the UAV123 video data is a
better fit in evaluating the performance of the proposed algorithm
than any other existing tracking datasets. This is because there are
many challenging scenes, e.g., abrupt scale/illumination
changes. Although we are primarily interested in developing an
algorithm for mobile, embedded robotic applications, it is important
to compare the performance of the proposed algorithm with those of the
state-of-the-art in nominal dataset for comparison. To this end, we
chose the OTB100 data that contains the videos recorded from smart
phones and typical cameras in perspective view.

Lastly, we tested the proposed algorithm on a temporally down-sampled
version of the UAV123 dataset, called UAV123$\_$10fps dataset. What we
would like to see from this experiment is to evaluate how robust the
proposed algorithm is to drastic motions of camera and targets.

{\it Burak: We have never told what EnKCF2 is before the following sentence. Just don't mention EnKCF2, but say a modification of EnKCF!}

\begin{comment}
Finally, the {\it E}nKCF2 is tested on temporally down-sampled version
of the UAV123 dataset, called UAV123$\_$10fps dataset.  This way, by
modifying the proposed {\it E}nKCF framework slightly we can tackle
scenarios dominated by extreme camera and object motion as we run
multiple correlation filter at each frame. One can also perform such
modifications based on the hardware specifications.  A more
sophisticated hardware can be more friendly to apply multiple
correlation filter ({\it E}nKCF2) at one frame whereas the ones on the
low end can only accommodate a single correlation filter at each frame
({\it E}nKCF).
\end{comment}

@@
